Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-11-24 Text/2024PresentationsChina.tex
Update slides: added densities for three tests

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{The test based on the Shannon entropy}
\centering
\includegraphics[width=0.7\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density-1}
\end{frame}
}

>>>>

%{\setbeamercolor{background canvas}{bg=anti-flashwhite}
%\begin{frame}{The test based on the Shannon entropy}
%\centering
%\includegraphics[width=0.7\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density-1}
%\end{frame}
%}
{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{The test based on the CV}
\centering
\includegraphics[width=0.9\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density_test_cv-1}
\end{frame}
}

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{The test based on the $\text{CV}_{\text{MnAD}}$}
\centering
\includegraphics[width=0.9\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density_test_MnAD-1}
\end{frame}
}

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{The test based on the Shannon entropy}
\centering
\includegraphics[width=0.9\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density_test_entropy-1}
\end{frame}
}
